\documentclass[main.tex]{subfiles}
 
\begin{document}
	\section{Hardware parts}
	\begin{enumerate}
		\item Spark V - NEX Robotics
		\item Xbee S2C Zigbee Module
		\item Camera - Intex 306IT 
		\item Laptop
	\end{enumerate}
	
	\subsection*{Spark V}
	\begin{flushleft}
		Spark V Robot \href{http://www.nex-robotics.com/products/spark-v-robot/spark-v.html}{\ExternalLink} is a low cost robot designed for robotics hobbyists and enthusiasts. It is jointly designed by NEX Robotics with Department of Computer Science and Engineering, IIT Bombay.
		
		Microcontroller: Atmel ATMega16A
		
		Refer the hardware \href{./datasheet/Spark V manuals/SPARK V ATMEGA16 Hardware Manual 2010-11-06.pdf}{\ExternalLink} and software\href{./datasheet/Spark V manuals/SPARK V ATMEGA16 Hardware Manual 2010-11-06.pdf}{\ExternalLink} manuals for more details.
	\end{flushleft}
	
	\section{Software}
	\subsection{IDEs used}
	\begin{enumerate}
		\item Atmel Studio V7 \href{http://www.atmel.com/microsite/atmel-studio/}{\ExternalLink}
		\item Pycharm 2016.2.3 \href{https://www.jetbrains.com/pycharm/download/#section=windows}{\ExternalLink}  
		\item Python IDLE v2.7.12
	\end{enumerate}			
	
	\subsection{Libraries used for Python v2.7.12}
	\begin{enumerate}
		\item OpenCV Version-3.2.7 \\
		Library used for image processing in python.
		\item OpenCV-contrib \href{https://github.com/skvark/opencv-python}{\ExternalLink}\\
		Wrapper package for OpenCV python bindings. This is used for aruco marker detection.
		\item Pyserial
		\item Numpy (1.12.1)
		\item XBee library
		\item Math library
	\end{enumerate}
	
	\subsection{Other Software}
	\begin{enumerate}
		\item PIP\\
		PIP is a package management system used to install and manage software packages written in Python.
		PIP is already installed if using Python 2.7.9 or Python 3.4 binaries downloaded from python.org, but you'll need to upgrade pip.
		\href{https://pip.pypa.io/en/stable/installing/}{\ExternalLink}
		\item XCTU\href{https://www.digi.com/products/xbee-rf-solutions/xctu-software/xctu}{\ExternalLink}\\
		Software used to configure Xbee modules
	\end{enumerate}	
\end{document}	